Fourmile Calibrations and Output

### 2025-05-21 fourmile_output_dec2024.Rmd
udpated kge vs bias and kge vs nse to add jitter

perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/all_kge.csv') %>%
  dplyr::select(year, model_run, value, metric)

perf <- perf %>%
  pivot_wider(names_from=metric,
               values_from=value)

nse_kge <- ggplot(perf, aes(x=kge, y=nse)) + 
  geom_point(size=1) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red") +
  theme_bw(base_size=20) # +
  # ylim(-0,1) +
  # xlim(0,1)

ggplotly(nse_kge)

ggplot(perf, aes(x=kge, y=pbias)) + 
  geom_point(size=1) +
  geom_abline(slope = 1, intercept = 0, linetype = "dashed", color = "red")

>>>>

perf <- read_csv('/Users/megansears/Documents/Repos/fourmile/38HRU_dec2024_updates/perf_metrics.csv')

perf <- perf %>%
  pivot_wider(names_from=metric,
               values_from=value) %>%
  filter(year == 'All')

perf1 <- perf %>%
  mutate(type = case_when(
    str_detect(model_run, "grid") ~ "Gridded",
    str_detect(model_run, "statn") ~ "Station"))

nse_kge <- ggplot(perf1, aes(x=KGE, y=NSE, color=type)) + 
  #geom_point(size=4, alpha=0.7) +
   geom_jitter(size = 4, alpha = 0.7, width = 0.05, height = 0.05) +
  theme_bw(base_size=20) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  theme(
    legend.position = 'bottom',
    legend.text = element_text(size = 16),
    legend.title = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    panel.grid.major.x = element_blank()  # remove vertical major grid lines
   # panel.grid.minor.x = element_blank(),
    #panel.grid.minor = element_blank()      # remove all minor grid lines

  )

nse_kge

pbias_kge <- ggplot(perf1, aes(x=KGE, y=pbias, color=type)) + 
  #geom_point(size=4, alpha=0.8) +
  geom_jitter(size = 4, alpha = 0.7, width = 0.001, height = 0.001) +
  theme_bw(base_size=20) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y = '% bias') +
  theme(
    legend.position = 'bottom',
    legend.text = element_text(size = 16),
    legend.title = element_blank(),
    panel.background = element_rect(fill = "white"),
    strip.background = element_blank(),
    text = element_text(color = "black"),
    axis.title = element_text(color = "black"),
    axis.text = element_text(color = "black"),
    panel.grid.major.x = element_blank()  # remove vertical major grid lines
   # panel.grid.minor.x = element_blank(),
    #panel.grid.minor = element_blank()      # remove all minor grid lines

  )

pbias_kge

library(patchwork)

combined_plot <- nse_kge + pbias_kge + 
  plot_layout(ncol = 2, guides = "collect") & 
  theme(legend.position = 'bottom')

combined_plot

ggsave('/Users/megansears/Documents/Repos/fourmile/figures/kge_nse_pbias.png',
       dpi=600,
       width=10,
       height=6)
